### 2011-07-13 Paper/Paper.tex
Updated paper, minor fix to code

NOTE(
Some music transcription
Performance rendering

YQX is state of the art

Rencon)

@@

The YQX system, as widmer admitted, tended to sometimes produce nervous sounding changes in expression. He presents two extensions that seek to generate smoother performances. The problem with these extensions is, as widmer admits himself, that the increased smoothness comes at the expense of expressitivity. To counter this, he adds three explicit rules that he uses to postprocess the performances. We think the reason that Widmer stumbled upon this tradeoff between expressiveness and nervousness because the nervousness is inherent to the way performances are generated at note-level. The system simply misses one component of expression, namely structure level expression. 
NOTE(that Widmer had to artificially introduce using rules. ) ?

@@

(The delta rule needs to be slightly modified to apply it to second order deltafunction, is this trivial?) ?

@@

\section{Implementation}
\section{Performance Rendering}
\begin{itemize}
\item Extract melody
\item Extract scorefeatures from melody
\item lookup notes in deviation, ignore missing notes
\item Extract expressive and non-expressive melody and extract expression features
\item Perform notes other than melody notes the same as the nearest melody note
\end{itemize}
\subsection{Dataset and representation}
\begin{itemize}
\item attack release
\item tempo curves
\end{itemize}
\subsection{Dealing with polyphony}
\subsection{Discretization}

Distinction of expressive tempo and attack and release.

>>>>

\begin{itemize}
\item Introduce performance rendering
\item Introduce YQX (What is it and why is it good)

\end{itemize}

@@

NOTE(Widmer didn't write the YQX paper, find out how to address the authors)

The YQX system, as Widmer admitted, tended to sometimes produce nervous sounding changes in expression. He presents two extensions that seek to generate smoother performances. The problem with these extensions is, as Widmer admits himself, that the increased smoothness comes at the expense of expressitivity. To counter this, he adds three explicit rules that he uses to postprocess the performances. We think the reason that Widmer stumbled upon this tradeoff between expressiveness and nervousness because the nervousness is inherent to the way performances are generated at note-level. The system simply misses one component of expression, namely structure level expression. 
NOTE(that Widmer had to artificially introduce using rules. ) ?

@@

NOTE(The delta rule needs to be slightly modified to apply it to second order deltafunction, is this trivial?) ?

@@

\section{Implementation}
\section{Performance Rendering}
\begin{itemize}
\item Extract melody
\item Extract scorefeatures from melody
\item lookup notes in deviation, ignore missing notes
\item Extract expressive and non-expressive melody and extract expression features
\item Perform notes other than melody notes the same as the nearest melody note
\end{itemize}
\subsection{Dataset and representation}
\begin{itemize}
\item attack release
\item tempo curves
\end{itemize}
\subsection{Dealing with polyphony}
\begin{itemize}
\item Use only melody
\end{itemize}
\subsection{Discretization}

\begin{itemize}
\item Normalize every feature
\item Discretization: int($\phi * d$) where d is the discretization parameter (the higher, the smaller the bins)
\end{itemize}

Discretization of expression is a delicate subject, we want to capture small changes in dynamics and tempo precisely, but outliers may fall in large bins. A sigmoid function is very useful for this purpose.

All expression parameters are ratios: their values vary around 1.0. To get a linear scale we use the logarithmic ratio. The tempo ratio is defined as: $\log(\frac{\texttt{performancetempo}}{\texttt{scoretempo}})$. To get the desired properties of discretization we use a sigmoid function. $D(p) = d * \frac{1}{1+e^{-p}}$ where $D(p)$ is the discretization of $p$, $e$ is the expression parameter value and $p$ is the discretization parameter.
